Open Clusters Characterization in Gaia DR2 Using ML Algorithms

### 2020-11-12 thesis/thesis.tex
thesis: Update References chapter

\usepackage{apacite}
\usepackage{caption}
\usepackage{eso-pic}
\usepackage{float}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{picture}
\usepackage{subcaption}

@@

However, as shown in Figures \ref{fig:pm_ngc_2682} and \ref{fig:parallax_ngc_2682}, in general it is not as easy and
becomes necessary to consider other parameters such as distances, or even metallicity and age (derived from isochrone curves)
and requires photometric data from stars in the studied field
\footnote{All figures have been sampled in order to reduce the document size, but are still a faithful representation of the original data}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/pm_ngc_2682.pdf}
      \caption{Proper motions}
      \label{fig:pm_ngc_2682}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/parallax_ngc_2682.pdf}
      \caption{Parallax}
      \label{fig:parallax_ngc_2682}
    \end{subfigure}
  \end{subfigure}
  \caption{Open Cluster NGC 2682}
\end{figure}

@@

\pagebreak

>>>>

\usepackage{apacite}
\usepackage{caption}
\usepackage{eso-pic}
\usepackage{float}
\usepackage{graphicx}
\usepackage{minted}
\usepackage[nottoc]{tocbibind}
\usepackage{picture}
\usepackage{subcaption}

@@

However, as shown in Figures \ref{fig:pm_ngc_6494} and \ref{fig:parallax_ngc_6494}, in general it is not as easy and
becomes necessary to consider other parameters such as distances, or even metallicity and age (derived from isochrone curves)
and requires photometric data from stars in the studied field
\footnote{All figures have been sampled in order to reduce the document size, but are still a faithful representation of the original data}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/pm_ngc_6494.pdf}
      \caption{Proper motions}
      \label{fig:pm_ngc_6494}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/parallax_ngc_6494.pdf}
      \caption{Parallax}
      \label{fig:parallax_ngc_6494}
    \end{subfigure}
  \end{subfigure}
  \caption{Open Cluster NGC 6494}
\end{figure}

@@

\newpage
